---
title: "`swissparl`: Example 4"
author: David Zumbach
date: December 14, 2019
output:
  md_document:
    variant: markdown_github
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 300, fig.width = 12, fig.height = 8, message = FALSE)
pacman::p_load(dplyr, ggplot2, hrbrthemes, quanteda, purrr, lubridate)
dfs <- readRDS("dfs.rds")
```

# What Are They Talking About?
Politicians talk a lot. *But how do we find out what the most important topics were?* The linguistic concept of [keyness](https://en.wikipedia.org/wiki/Keyword_(linguistics)) can serve as a simple starting point here. **Keyness** is the value for the statistical significance of the frequency of a word in a given corpus, related to a reference corpus. Let's take a look at this for the past years.   
We're downloading all the transcripts of the speeches (`Type = 1` prevents the download of notes on votes and other processes). For the sake of simplicity, we will only consider speeches in German during the analysis. The download still may take a few hours.

```{r g1, eval=FALSE}
df <- swissparl::get_data(
  table = "Transcript", 
  Language = "DE",
  Type = 1,
  LanguageOfText = "DE"
  )
```

Now we exclude all transcripts that come from Council Presidents and Vice-Presidents and then clean the texts with the help function `swissparl::clean_text`.

```{r g2, eval=FALSE}
# Package
library(dplyr)

# Data prep
dfs <- df %>%
  filter(!SpeakerLastName == "leer") %>% 
  filter(!SpeakerFunction %in% c("1VP-F", "1VP-M", "2VP-F", "2VP-M", "AP-M", "P-F", "P-M")) %>% 
  filter(!Function %in% c("1VP-M", "2VP-M", "P-F", "p-m", "P-m", "P-M", "P-MM")) %>% 
  mutate(Text2 = swissparl::clean_text(Text, keep_round_brackets = F))
```

## Document-Feature Matrix
With the help of the awesome [quanteda](https://quanteda.io/index.html) package, we convert the almost ~112,000 speeches into a [document-feature matrix](https://tutorials.quanteda.io/basic-operations/dfm/). This matrix then serves as the starting point for all further analyses.  

```{r g3}
# Packages
library(quanteda)
library(stringr)

# Create dfm
dfms <- corpus(
  dfs$Text2,
  docnames = dfs$ID,
  docvars = dfs %>% select(-Text, -Text2)
  ) %>% 
  dfm(
    tolower = F,
    remove = str_replace_all(stopwords("de"), "ß", "ss"),
    remove_punct = T
    )
```

## Custom Function
Now we're building a function that allows us to find out for a given year what the central keywords were compared to the rest of our corpus.

```{r g4}
get_keyness_per_year <- function(year, n = 30, nouns.only = T, no.names = T, dfm) {
  
  # Install package
  if (!require(lubridate)) install.package("lubridate")
  
  # Feedback
  cat(paste0("processing: '", year, "'\n"))

  # Keywords
  res <- quanteda::textstat_keyness(
    x = dfm,
    target = lubridate::year(quanteda::docvars(dfm)[["Start"]]) == year
    )
  
  # Only nouns
  if (nouns.only) res <- res %>% filter(!feature == tolower(feature)) 
  
  # No names
  if (no.names) res <- res %>% filter(!feature %in% c(quanteda::docvars(dfm)[["SpeakerLastName"]], quanteda::docvars(dfm)[["SpeakerFirstName"]])) 

  # Top N
  res %>% 
    dplyr::slice(1:n) %>% 
    dplyr::select(feature, chi2) %>% 
    dplyr::mutate(year = year)

}
```

We then apply this function to selected years and extract the 30 words with the highest keyness (*chi-squared test*)...

```{r g5}
keywords <- purrr::map_dfr(
  c(2001, 2003, 2005, 2007, 2009, 2011, 2013, 2015, 2017), 
  get_keyness_per_year, 
  dfm = dfms
  )
```

...and plot the results as wordclouds:

```{r g6}
# Packages
library(ggplot2)
library(hrbrthemes)
library(ggwordcloud)

# Plot
keywords %>%
  ggplot(aes(label = feature, size = chi2, alpha = 0.05 * chi2)) +
  geom_text_wordcloud() +
  labs(
    title = "What Are They Talking About?",
    subtitle = "Keywords of the Political Debates for Selected Years",
    caption = "Data: Parliamentary Services of the Federal Assembly, Bern"
    ) +
  facet_wrap(year~.) +
  theme_ipsum_rc()
```

## Comparison 2018/2019
Finally, we want to compare the last two years directly: We subset the dfm and then apply our function again. 

```{r g7}
# Data 
dfms2 <- dfms %>% 
  dfm_subset(year(docvars(dfms)[["Start"]]) %in% c(2018, 2019))

# Get 50 Keywords 
keywords2 <- purrr::map_dfr(c(2018, 2019), get_keyness_per_year, n = 50, dfm = dfms2)

# Plot
keywords2 %>%
  ggplot(aes(label = feature, size = chi2, alpha = 0.05 * chi2)) +
  geom_text_wordcloud() +
  scale_size_area(max_size = 14) +
  labs(
    title = "What Are They Talking About?",
    subtitle = "Keywords of the Political Debates, 2018 vs. 2019",
    caption = "Data: Parliamentary Services of the Federal Assembly, Bern"
    ) +
  facet_wrap(year~.) +
  theme_ipsum_rc()
```

Further analyses could now be performed using other NLP techniques, such as [Topic Modeling](https://cran.r-project.org/web/packages/tidytext/vignettes/topic_modeling.html).
